The large scale clustering in dispersion measure space

### 2015-05-06 writeup/dm_space_distortions.tex
Added sensitivity figure.

Description of the input power-spectra, $\bar n_f$ and figures.
Figure~\ref{f:n_f}

@@

@@

We assume that the survey will be shot noise dominated as would be the case for
an initial detection.  The noise powerspectrum on a shells with of width
$\Delta \chi$ is
\begin{equation}
    C^N_{\ell, ij} = \frac{\delta_{ij}}{\bar n_f(\chi_i)\chi_i^2\Delta\chi},
\end{equation}
Here, to indicate that we are now working with quantities binned in the radial
direction instead of
continuous functions, we've switched to $C_{\ell,ij}$ over 
$C_\ell(\chi, \chi')$. The error bar on the angular
cross-power spectrum is then
\begin{align}
    (\Delta{C^{ss}_{\ell,ij}})^2 = 
    \sqrt{\frac{1}{\ell(\ell + 1)\Delta \ell f_{\rm sky}}}
        \left[C^N_{\ell,ii} C^N_{\ell,jj} +  (C^N_{\ell,ij})^2\right],
\end{align}
where the second term in brackets only contributes for $i = j$.

To give an idea of the sensitivity of the survey, we collapse
$C^{ss}_{\ell,ij}$ to a single function of $\ell$ by taking a weighted average
of all pairs of radial bins. We use bin widths of $100\,{\rm MPc}/h$ over the
range $500\,{\rm MPc}/h$ to $3600\,{\rm MPc}/h$.
For weights in the radial bin average, we use the signal to noise-squared
at $\ell=100$, which extracts all the signal to noise at that $\ell$.
We exclude the $i = j$ bin pairs due to
the presumed observational complications discussed in the previous section.
This effectively discards the contribution from the local term.

>>>>

Description of the input power-spectra, $\bar n_f$ and figures.
Figure~\ref{f:n_f}, Figure~\ref{f:terms}.

@@

\begin{figure}
    \includegraphics[scale=0.42]{"figures/terms"}
    \caption{
        \label{f:terms}
        Terms in the DM-space cross-correlation angular power spectrum.
        All terms are evaluated at $\bar\chi=1000\,{\rm MPc}/h$ and 
        $\chi - \chi' = 10\,{\rm MPc}/h$, except the lowest most 
        ``local term'' curve which is for $\chi - \chi'=50\,{\rm MPc}/h$. 
        While
        the other two terms are highly insensitive to the separation of
        the radial slices, the local term drops rapidly at high separations.
    }
\end{figure}

@@

We assume that the survey will be shot noise dominated as would be the case for
an initial detection.  The noise powerspectrum on a shells with of width
$\Delta \chi$ is
\begin{equation}
    C^N_{\ell, ij} = \frac{\delta_{ij}}{\bar n_f(\chi_i)\chi_i^2\Delta\chi},
\end{equation}
Here, to indicate that we are now working with quantities binned in the radial
direction instead of
continuous functions, we've switched to $C_{\ell,ij}$ over 
$C_\ell(\chi, \chi')$. The uncertainty on the angular
cross-power spectrum is then
\begin{align}
    (\Delta{C^{ss}_{\ell,ij}})^2 = 
    {\frac{1}{\ell(\ell + 1)\Delta \ell f_{\rm sky}}}
        \left[C^N_{\ell,ii} C^N_{\ell,jj} +  (C^N_{\ell,ij})^2\right],
\end{align}
where the second term in brackets only contributes for $i = j$.

To give an idea of the sensitivity of the survey, we collapse
$C^{ss}_{\ell,ij}$ to a single function of $\ell$ by taking a weighted average
of all pairs of radial bins. We use bin widths of $100\,{\rm MPc}/h$ over the
range $500\,{\rm MPc}/h$ to $3500\,{\rm MPc}/h$.
For weights in the radial bin average, we use the signal to uncertainty-squared
at $\ell=100$, which extracts all the signal to noise at that $\ell$ and much
of it at other multipoles.
We exclude the $i = j$ bin pairs due to
the presumed observational complications discussed in the previous section.
This effectively discards the contribution from the local term. This is shown
in Figure~\ref{f:sensitivity}.

\begin{figure}
    \includegraphics[scale=0.42]{"figures/sensitivity"}
    \caption{
        \label{f:sensitivity}
        Sensitivity of a survey with $10^4$ dispersion measures distributed
        uniformly over half the sky.  Plotted is the cross-correlation
        power spectrum weighted averaged over all pairs of radial bins. Weights
        are chosen to maximize signal to noise at $\ell=100$.
    }
\end{figure}
